Constraining gravitational wave amplitude birefringence with GWTC-3

### 2022-08-12 src/tex/ms.tex
Update Graphs

Since Einstein proposed his theory of general relativity (GR), it was tested in a wide range of length scales.
After a century, we know that GR do not agree with quantum theories at some length scale.
To unify both theories, we need to study the possibility of different beyond-GR theories.
Some beyond-GR theories such as Chern-Simons theory (CS) suggested that there is gravitational wave (GW) amplitude birefringence,
while GR predicts there is no birefringence.

@@

For previous studies on the birefringence property such as \citet{Maria_2021}, the amplitude ratio depends on not only $\iota$,
but also the distance to the binary and the strength of the birefringence.
\begin{equation}
    \left(\frac{h_\mathrm{L_{obs}}}{h_\mathrm{R_{obs}}}\right)_\mathrm{Biref}^\mathrm{old}=\frac{e^{d_C\widetilde{\kappa}}\left(1-\cos\iota\right)^2}{e^{-d_C\widetilde{\kappa}}\left(1+\cos\iota\right)^2}\,,
\end{equation}where $d_C$ is the comoving distance to the binary, $\widetilde{\kappa}$ is the opacity parameter that represent
the strength of the birefringence with units of $L^{-1}$, and $h_\mathrm{L_{obs}}$ and $h_\mathrm{R_{obs}}$ are
the observed Fourier amplitude of left and right polarizations of the GW respectively. Note that GR is recovered if $\kappa$ is $0$.
This is a zeroth-order approximation of the birefringence model in CS, which assume there is no frequency dependence.
This would create a degeneracy between kappa and iota, as they can affect the amplitude ratio in the same way.

>>>>

Since Einstein proposed his theory of general relativity (GR), it was tested in a wide range of length scales.
After a century, we know that GR do not agree with quantum theories at some length scale.
To unify both theories, we need to study the possibility of different beyond-GR theories.
Some beyond-GR theories such as Chern-Simons gravity suggested that there is gravitational wave (GW) amplitude birefringence,
while GR predicts there is no birefringence.

@@

For previous studies on the birefringence property such as \citet{Maria_2021}, the amplitude ratio depends on not only $\iota$,
but also the distance to the binary and the strength of the birefringence.
\begin{equation}
    \left(\frac{h_\mathrm{L_{obs}}}{h_\mathrm{R_{obs}}}\right)_\mathrm{Biref}^\mathrm{old}=\frac{e^{d_C\widetilde{\kappa}}\left(1-\cos\iota\right)^2}{e^{-d_C\widetilde{\kappa}}\left(1+\cos\iota\right)^2}\,,
\end{equation}where $d_C$ is the comoving distance to the binary, $\widetilde{\kappa}$ is the opacity parameter that represent
the strength of the birefringence with units of $L^{-1}$, and $h_\mathrm{L_{obs}}$ and $h_\mathrm{R_{obs}}$ are
the observed Fourier amplitude of left and right polarizations of the GW respectively. Note that GR is recovered if $\kappa$ is $0$.
This is a zeroth-order approximation of the birefringence model in Chern-Simons gravity, which assume there is no frequency dependence.
This would create a degeneracy between kappa and iota, as they can affect the amplitude ratio in the same way.
